Hybrid Threads for the Parrot Virtual Machine

### 2012-06-05 Paper.tex
New section "Alarms and Timers"

>>>>

\section{Alarms and Timers}

Timers used for \textit{sleep}, alarms and preemption use a common timer thread implemented in \textit{src/alarm.c}. This thread sleeps until a new alarm is set or the currently active one expires. When the latter happens it increases the global alarm serial and notifies all threads that a timer is expired. Since it does not keep a list of pending alarms but knows only about the next one, interpreter threads are obliged to re-set their next alarms upon notification.
